The non-random assembly of functional motifs in plant-pollinator networks worldwide

### 2022-03-05 Manuscript/Main_text_Oikos.Rmd
Update on figure 2 with motifs, quite happy about the outcome!

library(ggforce) #workaround with ggforce to have facets with same sizes

p <- ggplot()+geom_point(data = d_2, aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                width=0.8,size=0.8,color="black") +theme_bw()+
  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
  theme( strip.background = element_blank())+
  theme(strip.text = element_text(face="bold", size=10, hjust=0),
        panel.border=element_rect(color="black",size=1.2))

>>>>

library(ggforce) #workaround with ggforce to have facets with same sizes 
library(ggtext)

labels <- c("2" = "*Motif 2* <img src='../Images/motif_2.png' width='22'/>" ,
          "3"= "*Motif 3* <img src='../Images/motif_3.png' width='22'/>",
          "4"= "*Motif 4* <img src='../Images/motif_4.png' width='22'/>",
          "5"= "*Motif 5* <img src='../Images/motif_5.png' width='22'/>",
          "6"= "*Motif 6* <img src='../Images/motif_6.png' width='22'/>",
          "7"= "*Motif 7* <img src='../Images/motif_7.png' width='22'/>",
          "8"= "*Motif 8* <img src='../Images/motif_8.png' width='22'/>",
          "9"= "*Motif 9* <img src='../Images/motif_9.png' width='22'/>",
          "10"= "*Motif 10* <img src='../Images/motif_10.png' width='22'/>",
          "11"= "*Motif 11* <img src='../Images/motif_11.png' width='22'/>",
          "12"= "*Motif 12* <img src='../Images/motif_12.png' width='22'/>",
          "13"= "*Motif 13* <img src='../Images/motif_13.png' width='22'/>",
          "14"= "*Motif 14* <img src='../Images/motif_14.png' width='22'/>",
          "15"= "*Motif 15* <img src='../Images/motif_15.png' width='22'/>",
          "16"= "*Motif 16* <img src='../Images/motif_16.png' width='22'/>",
          "17"= "*Motif 17* <img src='../Images/motif_17.png' width='22'/>")

p <- ggplot()+geom_point(data = d_2 , aes(y=factor(motif), 100*percentil_sizeclass), shape=21,color="black",fill="azure2",size=1.75, alpha=0.3)+
  geom_errorbar(data = d_2,aes(y = factor(motif), xmin=100*(mean-SE), xmax=100*(mean+SE)), 
                width=0.8,size=0.8,color="black") +theme_bw()+
  geom_point(data = d_2,aes(y = as.factor(motif), x=100*mean), 
             size=2,color="black")+labs(y="Two to five node motifs", x = "Percentile")+
  theme( strip.background = element_blank())+
  theme(strip.text = element_text(face="bold", size=10, hjust=0),
        panel.border=element_rect(color="black",size=1.2))+
  scale_y_discrete(name = NULL,
                   labels = labels) +
  theme(axis.text.y = ggtext::element_markdown())
